---
title: "BUSA8090 Assignment 3 Question 2"
author: "Prathamesh Devaraju"
date: "03/05/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries Used are as follows:
1. ggplot2: Used to plot data
2. tidyverse: Can be used to tidy up the data if required like for eg '%>%'
3. knitr, rmarkdown: It is to be used as the file is made into Rmarkdwon file format (.rmd) 
```{r}
library(ggplot2)
library(tidyverse)
library(knitr, rmarkdown)
```

```{r}
vaccine_rollout = data.frame(
  Countries = c("United States", "Australia", "China", "France", "India", "Turkey", "United Kingdom", "Germany", "Brazil"),
  Doses = c(213.39, 1.65, 195.02, 17.45, 127.13, 20.28, 43.46, 22.94, 33.81)
)
vaccine_rollout
summary(vaccine_rollout)
```
1. As we don't have any data set provided we have to generate a dataframe from the given graph in the question that have variables Countries and Doses. 'data.frame' is used to do so.
2. vaccine_rollout: It gives us the output in the tabular form so that further plots can be plotted.
3. Summary gives the type of class of variables, and will give all the basic statistical values of variables that are of type double, int.
```{r}
#Without stat='identity' ggplot wants to aggregate your data into counts.
Q2 = ggplot(vaccine_rollout, aes(x = fct_reorder(Countries,Doses), y = Doses))+
     geom_bar(stat = 'identity', aes(fill = Doses))+
     coord_flip()+
     xlab("Countries")+
     ylab("Doses(per million)")+
     labs(title = "BUSA8090 Assignment 3 Question 2",
       subtitle = "COVID-19 Vaccine Doses Administered, April 20 2021",
       caption = "Total Number Of vaccination Doses Administered")+
     geom_text(aes(label=paste(Doses, "million"), y=200), hjust=0.5, color="red", size=05)+
     theme(plot.title = element_text(size = 20),
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 15),
        text = element_text(size=15, colour = "black"),
        axis.text.x = element_text(size=15),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15),
        )


Q2

```

1. 'ggplot(vaccine_rollout, aes(x = fct_reorder(Countries,Doses), y = Doses))+': In this piece of code the dataframe vaccine_rollout is used to plot a bar plot. Here we will have to do a fct_reorder to plot the x-axis. 
    fct_reorder is useful for 1d displays where factor i.e Doses will be mapped to the position in ascending order of doses that have been rolled out by a respective country. 
    As we are plotting a horizontal Bar plot our X-axis and Y-axis will be interchanged so in this our Y-axis will be 'Doses'. '+' operator is used as pipe so that more objects or customization can be added in the plot.

2. 'geom_bar(stat = 'identity', aes(fill = Doses))+': geom_bar is used to plot a bar plot. Here if we don't use 'stat = 'identity'' then ggplot will aggregate the data into counts. 
    aes(fill = Doses)' will fill the barchart in the differnt shades of blue and there is no need to specify any color pallete using colour_brewer because if nothing is specified ggplot takes shades of blue as a default colour.

3. 'coord_flip()': This function flips the plot into horizaontal plot.

4. xlab("Countries"): This is used to give a label to X-axis.

5. ylab("Doses(per million)"): This is used to give a label to Y-axis.

6. labs(title = "BUSA8090 Assignment 3 Question 2",
       subtitle = "COVID-19 Vaccine Doses Administered, April 20 2021",
       caption = "Total Number Of vaccination Doses Administered"):
   The above codes are written to give the barplot Title, Subtitle and caption So as to make the      plot more descriptive.
   
7. 'geom_text(aes(label=paste(Doses, "million"), y=200), hjust=0.5, color="red", size=05)+': This piece of code is written so that the exact number of doses rolled out appear on the barplot. 
    As it is used to improve aesthetics of the barplot 'aes' is used. Further 'label=paste(Doses,"million")' is used. Where paste is used so that every entry gets "million" in the end. 
    'y=200' is done so that all of the specific barchart entries get aligned and the bar plot will look good. 'hjust=0.5' is used to align the text horizontally and its value is set to 0.5 which
    means that the text is centrally aligned to the axis. 'color="red"' to change the colour of the     number of doses. 'size=05' changes the font size of the number of doses rolled out.

8. 'theme(plot.title = element_text(size = 20),
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 15),
        text = element_text(size=15, colour = "black"),
        axis.text.x = element_text(size=15),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15),
        )': This chunk of code is mainly to change the themes of the axis-names, title, subtitles,legend title, legendtext fonts, colour of the text.
```{r}
ggsave("Q2.png", width = 15, height = 10, limitsize = FALSE)
```
ggsave is used to save the code in the working directory or in the location where .R or .Rmd file is already saved.
